Viscous Erosion in Porous Media

### 2018-03-12 docs/methods/erosion_methods.tex
NM
small edits to text

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Erosion Model} 
\label{sec:erosion}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary Integral Equation Formulation} 
\label{sec:bies}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Computing the Shear Stress}
\label{sec:shearStressLP}
To compute the shear stress, there are two options.  First, instead of
solving the BIE~\eqref{eqn:completed_BIE} for an arbitrary density
function, a similar BIE can be solved for the
traction~\cite{mit-spa2016}.  Alternatively, the traction corresponding
to the double-layer potential of the velocity~\eqref{eqn:velocityDLP}
can be computed using appropriate layer potentials.  While the first
method bypasses a step by not forming a density function, this method
does not allow us to compute other quantities such as the vorticity.
Therefore, we use the second method.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Methods}
\label{s:method}
There are three main numerical methods that need to be developed.  In
Section~\ref{sec:BIE}, we describe how the BIE~\eqref{eqn:completed_BIE}
is solved.  Once the density function is found,
Section~\ref{sec:shearStress} describes how the shear
stress~\eqref{eqn:shearStressLP} is computed.  Then, in
Section~\ref{sec:timeStepping}, a time stepping method for evolving the
interface according to equations~\eqref{eqn:Levo1}
and~\eqref{eqn:thetaevo1} are described. So that we can form stable
simulations with long time horizons, we use numerical methods that
achieve spectral accuracy in space, second-order accuracy in time, and
maintain an equispaced discretization of the bodies.  The boundaries are
represented in Fourier space, giving us a set of discretization points
$\xx_i$ of each body, and all derivatives and integrals (the arclength,
curvature, and mean values) are computed with spectral accuracy using
the Fourier representation.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Shear Stress}
\label{sec:shearStress}
We have decomposed the deformation tensor into the contributions due to
three different terms.  The contributions from the Stokeslets and the
rotlets can be directly evaluated since $\rr \neq 0$ for all $\xx \in
\gamma$.  For the layer potential term, we would like to use the
trapezoid rule, but the kernel of the deformation tensor due to the
double-layer potential~\eqref{eqn:shearStressDLP} 
\begin{align*}
  K_\ssigma(\xx,\yy)\eeta(\yy) &= \frac{1}{2\pi} \left(
    2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn)
    \right. \\ & \hspace{25pt}+ \left.
    \frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
    8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
  \right),
\end{align*}
has a singularity that is asymptotic to $\bigO(\rho^{-2})$ when $\yy
\rightarrow \xx$.  The singularity strength can be reduced since the
velocity corresponding to a constant density function is
constant~\cite{poz1992}.  Therefore, the deformation tensor of the
double-layer potential is equivalent to
\begin{align*}
  \ssigma^{\DD}(\xx) = \int_{\bd\Omega}K_\ssigma(\xx,\yy)
      (\eeta(\yy) - \eeta(\xx)) \, ds_{\yy}, \quad \xx \in \bd\Omega.
\end{align*}
This expression for the deformation tensor has a singularity that is
asymptotic to $\bigO(\rho^{-1})$ when $\yy \rightarrow \xx$.  Finally,
to achieve spectral accuracy, we apply odd-even
integration~\cite{sid-isr1988}.  Therefore, the deformation tensor of
the double-layer potential at a discretization point $\xx_i$ on body
$\gamma_\ell$, with $i$ being odd, is approximated as
\begin{align}
  \ssigma^{\DD}(\xx_i) = \sum_{\xx_j \notin \gamma_\ell}
    K_\ssigma(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_j + 
  \sum_{\substack{\xx_j \in \gamma_\ell \\ j \: \mathtt{even}}}
    K_\ssigma(\xx_i,\xx_j) (\eeta(\xx_j) - \eeta(\xx_i)) \Delta s_j,
  \label{eqn:stressOddEven}
\end{align}
and a similar approximation is used when $i$ is even.  The deformation
tensor due to the Stokeslets and rotlets are given in
equation~\eqref{eqn:shearStressSR}.  Finally, the jump in the
deformation tensor~\eqref{eqn:shearStressJump} is computed with Fourier
differentiation.  Then, the shear stress is computed by multiplying the
deformation tensor by the normal vector, and taking the inner product
with the tangent vector.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Post Processing Quantities of Interest}
\label{s:qoi}
To study characteristics of the flow, the vorticity
(Section~\ref{sec:vorticity}), pressure (Section~\ref{sec:pressure}),
and drag (Section~\ref{sec:drag}) will be computed.  Once
equation~\eqref{eqn:completed_DLP} is solved for the density function,
Stokeslets, and rotlets, all of these quantities can be computed.  For
target points in the fluid domain, the resulting layer potentials
involve integrands that are periodic, so the trapezoid rule guarantees
spectral accuracy since the integrand is smooth~\cite{tre-wei2014}.
However, if the target point is close to a boundary, a nearly-singular
integrand must be integrated, and this requires upsampling that is
described in Section~\ref{sec:NSI}.  When the target points is on the
boundary, the integrands involve singularities that are evaluated by
combining singularity subtraction and odd-even
integration~\cite{sid-isr1988}.

@@

%%-----------------------------------------------------------------%%
% RESULTS SECTION
%%-----------------------------------------------------------------%%
\section{Results: single-body erosion}
\label{SingleResults}
With the description of the methods complete, we now present numerical results on bodies eroding in Stokes flow. We first discuss the case of a single body, as certain features can be predicted analytically and thus used for validation. In Section \ref{MultiResults} we will discuss the erosion of multiple bodies and highlight important differences that arise compared to the single-body case.

@@

Figure~\ref{shrink_intface}(a) shows that the spacing between successive interfaces becomes larger with time, suggesting that the overall shear stress is increasing as the body vanishes. This observation is consistent with the well-known 3D Stokes drag law, $\tau \sim \mu \umax / a$, in which drag is inversely proportional to body-scale $a$ (e.g.~for a sphere, $a$ is taken to be the radius). This law must be modified in two dimensions, though. The modification is made non-trivial by subtleties of the 2D Stokes paradox, but can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory \cite{poz1997, bouzarth2007epicyclic, camassa2008trajectory, MooreJFM2012, zhao2015transportation}. 
For a slender body in flow perpendicular to its long-axis $\ell$, the drag is proportional to
$\mu \umax \ell/ \log(\ell/a)$, where $a$ is a lengthscale of the cross-section and $a \ll \ell$. This relationship implies that the stress per unit span on a 2D cross-section can be estimated by
\begin{align}
  \label{eqn:stresslaw}
  \tau \sim \frac{\mu \umax}{a \log(\ell/a)} \qquad \text{for } a \ll \ell \, .
\end{align}
In interpreting our 2D simulations, we will treat the span, $\ell$, as fixed. Recall that $L$ denotes the total perimeter of the cross-section, and therefore $a$ and $L$ can often be used interchangeable in scaling analysis, since they each represent a lengthscale of the cross-section.

@@

The body's rate of area reduction is given by integrating the absolute shear stress around the boundary
\begin{align}
\dot{A} = - \int_{\gamma} \atau \, ds \,  = - \mean{\atau} L \, .
\end{align}
Thus, the area-loss rate is given by the product of the mean shear
$\mean{\atau}$ and the total perimeter $L$, which is an exact relationship. Inserting scaling law~\eqref{eqn:stresslaw} gives
\begin{align}
\dot{A} \sim \frac{ - \mu \umax}{\log(\ell/a)} \qquad \text{as } a \to 0 \, . 
\end{align}
Noting that $A \sim a^2$ allows one to solve the ODE to determine how the body area changes with time
\begin{align}
\label{area_predict}
\frac{A}{A_0} \left( 1 - c_1 \log{\frac{A}{A_0}} \right) \sim \frac{t_f - t}{t_f} \quad \text{as } t \to t_f \, .
\end{align}
Here, $t_f$ is the time of vanishing, $A_0$ is the body's initial area, and $c_1$ is a free constant. The above is an {\em implicit} relationship for how the area scales down in time during erosion. In Fig.~\ref{area_drag}a, we show the body area as a function of time measured in the simulation against the above scaling law with $c_1 = 0.24$ a fit parameter. The comparison shows close agreement between the two (they are indistinguishable).

@@

As a final check, we can estimate the drag (per unit span) using slender-body theory via the formula
\begin{align}
\label{dragscaling}
\frac{F_D}{4 \pi} \sim \frac{ \mu U}{\log(\ell/a)}
\end{align}
For a {\em circular} cylinder, $a$ is the radius and the normalization factor $4 \pi$ is exact within the slender-body framework. To generalize to other shapes, we define $a = \sqrt{A/\pi}$ and fit $\ell$ to get $\ell = 2.3 a_0$.

@@

With the vanishing rate understood, we now seek to quantify the limiting shape observed in Fig.~\ref{shrink_intface}(a). Certain features of this shape can be predicted analytically by appealing to the principal that, in long time, the shear stress becomes uniformly distributed along the body. In particular, consider the angle formed at the front and rear stagnation points. In a small region around this point, we can neglect body curvature and consider the problem of Stokes flow around an infinite wedge. We aim to determine the wedge's opening angle, $\oangle$, through the principle of uniform stress. Exact solutions can be obtained to this problem via separation of variables in polar coordinates $(r, \theta)$~\cite{poz1997}. In this section alone, $\theta$ denotes the polar coordinate (not the local tangent angle along the body). The corresponding stream function is assumed to take the form $\psi = r^{\lambda}f(\theta)$, with $\Delta^2 \psi = 0$, which gives the 4th order ODE~\cite{poz1997}
\begin{align*}
  f'''' + 2(\lambda^2 - 2 \lambda + 2)f'' + \lambda^2(\lambda-2)^2 f = 0
\end{align*}

@@

This ODE is subject to no-slip boundary conditions along the wedge $f(\thb) = f'(\thb) = 0$, where $\thb = \pi - \oangle/2$, along with the condition of odd-symmetry $f(0) = f''(0) = 0$ (corresponding to up-down symmetry of the flow).  The corresponding shear stress evaluated on the surface of the wedge is $\tau = \mu r^{\lambda-2} f''(\thb)$. Thus, the wedge of uniform stress corresponds to $\lambda = 2$. For this value, the solution for $f$ satisfying odd symmetry is
\begin{align*}
  f(\theta) = B \sin (2 \theta) + C \theta
\end{align*}
Imposing the no-slip boundary conditions gives the condition
\begin{align*}
  \sin(2 \thb) - 2 \thb \cos(2 \thb) = 0
\end{align*}
which has a solution $\thb \approx 129$ degrees. This gives an opening angle of $\oangle = 2(180^{\circ} - \thb) \approx 102$ degrees. 
% Pozrikidis page 239: symmetric flow.

@@

To compare with this analytical prediction, we aim to measure the opening angles formed in our numerical simulations. However, our simulations lose accuracy just in the final moments as the body is vanishing due to the shear stress blowing up (in accordance with the scaling laws discussed in Section \ref{sec:scaling}). To circumvent this problem, we could restart our simulation with a scaled-up version of the the near-final  body as the initial condition and iterate the process until convergence. A simpler solution, though, is to remove the effect of shrinking by modifying the normal velocity $\Vn$ to have zero mean,
\begin{align*}
\Vn \leftarrow \Vn - \mean{\Vn} \, .
\end{align*}
This modification allows erosion sculpt the body as it normally would but artificially keeps the area fixed. We show in Fig.~\ref{fixed_intface}(a) several interfaces of this modified erosion process at equally-spaced times. Notice the body obtains a similar profile as observed previously, but with fixed area. Importantly, more numerical accuracy is now available to quantify the terminal state. The inset in Fig.~\ref{fixed_intface}(a) shows a zoom of the body's rear stagnation point, demonstrating that the near-corner is actually smooth on a fine scale, in accordance with our numerical smoothing. 
Likewise, Fig.~\ref{fixed_intface}(b) shows the stress distribution on the evolving body, revealing that stress becomes more uniform as time proceeds. Interestingly, the slight rise in shear near the front/rear corners that was seen in Fig.~\ref{shrink_intface}(b) is no longer present, suggesting that the effect was due to loss of accuracy.
Here, time is normalized by the same vanishing time $t_f = 1.79E-2$ as in Fig.~\ref{shrink_intface}. Curiously, about 3 multiples of $t_f$ are required to reach an approximate steady-state, which contrasts with previous studies of high-Reynold's-number erosion, in which a satisfactory steady-state was usually reached before the body vanished~\cite{moo-ris-chi-zha-she2013}.

@@

To examine the influence of the smoothing parameters, $\eps$ and $\sigma$, we show in Table~\ref{table:arangle} the measurements of aspect ratio and opening angle for different simulations. We fix the total number of discretization points at $N_\iin = 1024$ and sequentially reduce the smoothing with $\eps$ and $\sigma$ always equal. We choose the values $20/1024$, $10/1024$, and $5/1024$. 
Loosely, this corresponds to smoothing over the nearest 20, 10, and 5 grid points respectively. As seen in the table, the aspect ratio converges to a values of $2.65$ and the opening angle converges to $102^{\circ}$. We also estimate the uncertainty in the angle measurements by varying the region of the polynomial fit and the degree of the fit. As shown in the table, as the smoothing parameters are reduced, the angle measurements become more precise.

@@

\section{Results: multi-body erosion}
\label{MultiResults}

@@

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.99 \textwidth]{./figs/06plots.pdf}
\caption{\label{fig:06plots} plots to go with 6 body simulation.
}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure generated from data file 50circ512p5, 
%which uses 50circ512.in with epsfac = 30, sigfac = 10, dt = 1e-4, fixpdrop = 1

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Erosion model} 
\label{sec:erosion}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary integral equation formulation} 
\label{sec:bies}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Computing the shear stress}
\label{sec:shearStressLP}
To compute the shear stress, there are two options.  First, instead of
solving the BIE~\eqref{eqn:completed_BIE} for an arbitrary density
function, a similar BIE can be solved for the
traction~\cite{mit-spa2016}.  Alternatively, the traction corresponding
to the double-layer potential of the velocity~\eqref{eqn:velocityDLP}
can be computed using appropriate layer potentials.  While the first
method bypasses a step by not forming a density function, this method
does not allow us to compute other quantities such as the vorticity.
Therefore, we use the second method.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical methods}
\label{s:method}
There are three main numerical methods that need to be developed.  In
Section~\ref{sec:BIE}, we describe how the BIE~\eqref{eqn:completed_BIE}
is solved.  Once the density function is found,
Section~\ref{sec:shearStress} describes how the shear
stress~\eqref{eqn:shearStressLP} is computed.  Then, in
Section~\ref{sec:timeStepping}, a time stepping method for evolving the
interface according to equations~\eqref{eqn:Levo1}
and~\eqref{eqn:thetaevo1} are described. So that we can form stable
simulations with long time horizons, we use numerical methods that
achieve spectral accuracy in space, second-order accuracy in time, and
maintain an equispaced discretization of the bodies.  The boundaries are
represented in Fourier space, giving us a set of discretization points
$\xx_i$ of each body, and all derivatives and integrals (the arclength,
curvature, and mean values) are computed with spectral accuracy using
the Fourier representation.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Shear stress}
\label{sec:shearStress}
We have decomposed the deformation tensor into the contributions due to
three different terms.  The contributions from the Stokeslets and the
rotlets can be directly evaluated since $\rr \neq 0$ for all $\xx \in
\gamma$.  For the layer potential term, we would like to use the
trapezoid rule, but the kernel of the deformation tensor due to the
double-layer potential~\eqref{eqn:shearStressDLP} 
\begin{align*}
  K_\ssigma(\xx,\yy)\eeta(\yy) &= \frac{1}{2\pi} \left(
    2\frac{\rr \cdot \nn}{\rho^2} \frac{\rr \cdot \eeta}{\rho^2} \II + 
    \frac{\rr \cdot \eeta}{\rho^4} (\nn \otimes \rr + \rr \otimes \nn)
    \right. \\ & \hspace{25pt}+ \left.
    \frac{\rr \cdot \nn}{\rho^4} (\eeta \otimes \rr + \rr \otimes \eeta) - 
    8\frac{(\rr \cdot \nn)(\rr \cdot \eeta)}{\rho^6}(\rr \otimes \rr)
  \right),
\end{align*}
has a singularity that is asymptotic to $\bigO(\rho^{-2})$ when $\yy
\rightarrow \xx$.  The singularity strength can be reduced since the
velocity corresponding to a constant density function is
constant~\cite{poz1992}.  Therefore, the deformation tensor of the
double-layer potential is equivalent to
\begin{align*}
  \ssigma^{\DD}(\xx) = \int_{\bd\Omega}K_\ssigma(\xx,\yy)
      (\eeta(\yy) - \eeta(\xx)) \, ds_{\yy}, \quad \xx \in \bd\Omega.
\end{align*}
This expression for the deformation tensor has a singularity that is
asymptotic to $\bigO(\rho^{-1})$ when $\yy \rightarrow \xx$.  Finally,
to achieve spectral accuracy, we apply odd-even
integration~\cite{sid-isr1988}.  Therefore, the deformation tensor of
the double-layer potential at a discretization point $\xx_i$ on body
$\gamma_\ell$, with $i$ being odd, is approximated as
\begin{align}
  \ssigma^{\DD}(\xx_i) = \sum_{\xx_j \notin \gamma_\ell}
    K_\ssigma(\xx_i,\xx_j) \eeta(\xx_j) \Delta s_j + 
  \sum_{\substack{\xx_j \in \gamma_\ell \\ j \: \mathtt{even}}}
    K_\ssigma(\xx_i,\xx_j) (\eeta(\xx_j) - \eeta(\xx_i)) \Delta s_j,
  \label{eqn:stressOddEven}
\end{align}
and a similar approximation is used when $i$ is even.  The deformation
tensor due to the Stokeslets and rotlets are given in
equation~\eqref{eqn:shearStressSR}.  Finally, the jump in the
deformation tensor~\eqref{eqn:shearStressJump} is computed with Fourier
differentiation.  Then, the shear stress is computed by multiplying the
deformation tensor by the normal vector, and taking the inner product
with the tangent vector.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Post processing quantities of interest}
\label{s:qoi}
To study characteristics of the flow, the vorticity
(Section~\ref{sec:vorticity}), pressure (Section~\ref{sec:pressure}),
and drag (Section~\ref{sec:drag}) will be computed.  Once
equation~\eqref{eqn:completed_DLP} is solved for the density function,
Stokeslets, and rotlets, all of these quantities can be computed.  For
target points in the fluid domain, the resulting layer potentials
involve integrands that are periodic, so the trapezoid rule guarantees
spectral accuracy since the integrand is smooth~\cite{tre-wei2014}.
However, if the target point is close to a boundary, a nearly-singular
integrand must be integrated, and this requires upsampling that is
described in Section~\ref{sec:NSI}.  When the target points is on the
boundary, the integrands involve singularities that are evaluated by
combining singularity subtraction and odd-even
integration~\cite{sid-isr1988}.

@@

%%-----------------------------------------------------------------%%
% RESULTS SECTION
%%-----------------------------------------------------------------%%
\section{Results: Single-body erosion}
\label{SingleResults}
With the description of the methods complete, we now present numerical results on bodies eroding in Stokes flow. We first discuss the case of a single body, as certain features can be predicted analytically and thus used for validation. In Section \ref{MultiResults} we will discuss the erosion of multiple bodies and highlight important differences that arise compared to the single-body case.

@@

Figure~\ref{shrink_intface}(a) shows that the spacing between successive interfaces becomes larger with time, suggesting that the overall shear stress is increasing as the body vanishes. This observation is consistent with the well-known 3D Stokes drag law, $\tau \sim \mu \umax / a$, in which drag is inversely proportional to body-scale $a$ (e.g.~for a sphere, $a$ is taken to be the radius). This law must be modified in two dimensions, though. The modification is made non-trivial by subtleties of the 2D Stokes paradox, but can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory \cite{poz1997, bouzarth2007epicyclic, camassa2008trajectory, MooreJFM2012, zhao2015transportation}. 
For a slender body in flow perpendicular to its long-axis $\ell$, the drag is proportional to
$\mu \umax \ell/ \log(\ell/a)$, where $a$ is a length scale of the cross-section and $a \ll \ell$. This relationship implies that the stress per unit span on a 2D cross-section can be estimated by
\begin{align}
  \label{eqn:stresslaw}
  \tau \sim \frac{\mu \umax}{a \log(\ell/a)} \qquad \text{for } a \ll \ell \, .
\end{align}
In interpreting our 2D simulations, we will treat the span, $\ell$, as
fixed. Recall that $L$ denotes the total perimeter of the cross-section,
and therefore $a$ and $L$ can often be used interchangeable in scaling
analysis, since they each represent a length scale of the cross-section.

@@

The body's rate of area reduction is given by integrating the absolute shear stress around the boundary
\begin{align}
\dot{A} = - \int_{\gamma} \atau \, ds \,  = - \mean{\atau} L \, .
\end{align}
Thus, the area-loss rate is given by the product of the mean shear
$\mean{\atau}$ and the total perimeter $L$, which is an exact relationship. Inserting scaling law~\eqref{eqn:stresslaw} gives
\begin{align}
\dot{A} \sim \frac{ - \mu \umax}{\log(\ell/a)} \qquad \text{as } a \to 0 \, . 
\end{align}
Noting that $A \sim a^2$ allows one to solve the ODE to determine how the body area changes with time
\begin{align}
\label{area_predict}
\frac{A}{A_0} \left( 1 - c_1 \log{\frac{A}{A_0}} \right) \sim \frac{t_f - t}{t_f} \quad \text{as } t \to t_f \, .
\end{align}
Here, $t_f$ is the time of vanishing, $A_0$ is the body's initial area,
and $c_1$ is a free constant. The above is an {\em implicit}
relationship for how the area scales down in time during erosion. In
Fig.~\ref{area_drag}(a), we show the body area as a function of time measured in the simulation against the above scaling law with $c_1 = 0.24$ a fit parameter. The comparison shows close agreement between the two (they are indistinguishable).

@@

As a final check, we can estimate the drag (per unit span) using slender-body theory via the formula
\begin{align}
\label{dragscaling}
\frac{F_D}{4 \pi} \sim \frac{ \mu U}{\log(\ell/a)}.
\end{align}
For a {\em circular} cylinder, $a$ is the radius and the normalization factor $4 \pi$ is exact within the slender-body framework. To generalize to other shapes, we define $a = \sqrt{A/\pi}$ and fit $\ell$ to get $\ell = 2.3 a_0$.

@@

With the vanishing rate understood, we now seek to quantify the limiting shape observed in Fig.~\ref{shrink_intface}(a). Certain features of this shape can be predicted analytically by appealing to the principal that, in long time, the shear stress becomes uniformly distributed along the body. In particular, consider the angle formed at the front and rear stagnation points. In a small region around this point, we can neglect body curvature and consider the problem of Stokes flow around an infinite wedge. We aim to determine the wedge's opening angle, $\oangle$, through the principle of uniform stress. Exact solutions can be obtained to this problem via separation of variables in polar coordinates $(r, \theta)$~\cite{poz1997}. In this section alone, $\theta$ denotes the polar coordinate (not the local tangent angle along the body). The corresponding stream function is assumed to take the form $\psi = r^{\lambda}f(\theta)$, with $\Delta^2 \psi = 0$, which gives the 4th order ODE~\cite{poz1997}
\begin{align*}
  f'''' + 2(\lambda^2 - 2 \lambda + 2)f'' + \lambda^2(\lambda-2)^2 f =
  0.
\end{align*}

@@

This ODE is subject to no-slip boundary conditions along the wedge $f(\thb) = f'(\thb) = 0$, where $\thb = \pi - \oangle/2$, along with the condition of odd-symmetry $f(0) = f''(0) = 0$ (corresponding to up-down symmetry of the flow).  The corresponding shear stress evaluated on the surface of the wedge is $\tau = \mu r^{\lambda-2} f''(\thb)$. Thus, the wedge of uniform stress corresponds to $\lambda = 2$. For this value, the solution for $f$ satisfying odd symmetry is
\begin{align*}
  f(\theta) = B \sin (2 \theta) + C \theta.
\end{align*}
Imposing the no-slip boundary conditions gives the condition
\begin{align*}
  \sin(2 \thb) - 2 \thb \cos(2 \thb) = 0,
\end{align*}
which has a solution $\thb \approx 129$ degrees. This gives an opening angle of $\oangle = 2(180^{\circ} - \thb) \approx 102$ degrees. 
% Pozrikidis page 239: symmetric flow.

@@

To compare with this analytical prediction, we aim to measure the opening angles formed in our numerical simulations. However, our simulations lose accuracy just in the final moments as the body is vanishing due to the shear stress blowing up (in accordance with the scaling laws discussed in Section \ref{sec:scaling}). To circumvent this problem, we could restart our simulation with a scaled-up version of the the near-final  body as the initial condition and iterate the process until convergence. A simpler solution, though, is to remove the effect of shrinking by modifying the normal velocity $\Vn$ to have zero mean,
\begin{align*}
\Vn \leftarrow \Vn - \mean{\Vn} \, .
\end{align*}
This modification allows erosion to sculpt the body as it normally would but artificially keeps the area fixed. We show in Fig.~\ref{fixed_intface}(a) several interfaces of this modified erosion process at equally-spaced times. Notice the body obtains a similar profile as observed previously, but with fixed area. Importantly, more numerical accuracy is now available to quantify the terminal state. The inset in Fig.~\ref{fixed_intface}(a) shows a zoom of the body's rear stagnation point, demonstrating that the near-corner is actually smooth on a fine scale, in accordance with our numerical smoothing. 
Likewise, Fig.~\ref{fixed_intface}(b) shows the stress distribution on the evolving body, revealing that stress becomes more uniform as time proceeds. Interestingly, the slight rise in shear near the front/rear corners that was seen in Fig.~\ref{shrink_intface}(b) is no longer present, suggesting that the effect was due to loss of accuracy.
Here, time is normalized by the same vanishing time $t_f = 1.79E-2$ as in Fig.~\ref{shrink_intface}. Curiously, about 3 multiples of $t_f$ are required to reach an approximate steady-state, which contrasts with previous studies of high-Reynolds-number erosion, in which a satisfactory steady-state was usually reached before the body vanished~\cite{moo-ris-chi-zha-she2013}.

@@

To examine the influence of the smoothing parameters, $\eps$ and
$\sigma$, we show in Table~\ref{table:arangle} the measurements of the
aspect ratio and the opening angle for different simulations. We fix the total number of discretization points at $N_\iin = 1024$ and sequentially reduce the smoothing with $\eps$ and $\sigma$ always equal. We choose the values $20/1024$, $10/1024$, and $5/1024$. 
Loosely, this corresponds to smoothing over the nearest 20, 10, and 5 grid points respectively. As seen in the table, the aspect ratio converges to a values of $2.65$ and the opening angle converges to $102^{\circ}$. We also estimate the uncertainty in the angle measurements by varying the region of the polynomial fit and the degree of the fit. As shown in the table, as the smoothing parameters are reduced, the angle measurements become more precise.

@@

\section{Results: Multi-body erosion}
\label{MultiResults}

@@

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.85 \textwidth]{./figs/06plots.pdf}
\caption{\label{fig:06plots} plots to go with 6 body simulation.
}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure generated from data file 50circ512p5, 
%which uses 50circ512.in with epsfac = 30, sigfac = 10, dt = 1e-4, fixpdrop = 1
